MaxEnt: What is it good for?

### 2015-08-10 ms.tex
Fixed wording

There are several possible reasons for the lack of consensus. 
One is that the name ``MaxEnt'' has been used to refer not just to the principle
for updating probability distributions, but also to a specific choice of
regularisation term in optimisation-based methods for inverse problems
\citep{}, among other things. Since Bayesian inference is
a more principled way to deal with the uncertainty than regularised
optimisation, this leads to the idea that Bayesian inference
{\it supersedes} MaxEnt, and therefore that MaxEnt can be ignored.

In addition, many defences and explanations of MaxEnt in the literature
are weak.

>>>>

There are several possible reasons for the lack of consensus. 
One is that the name ``MaxEnt'' has been used to refer not just to the principle
for updating probability distributions, but also to a specific choice of
regularisation term in optimisation-based methods for inverse problems
\citep{}, among other things. Since Bayesian inference is
a more principled way to deal with the uncertainty than regularised
optimisation, MaxEnt seems obsolete --- although it is obvious that
an argument against one idea does not imply much about another idea that
happens to share the same name.
In addition, many defences and explanations of MaxEnt in the literature
are weak.
